
\documentclass[a4paper,10pt]{article}
\usepackage{fullpage}
\sloppy
\usepackage[none]{hyphenat}
\hyphenpenalty=10000
\exhyphenpenalty=10000

\usepackage[top=0in, bottom=.5in, left=.25in, right=.25in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{array}
\usepackage{titlesec}

\titlespacing{\section}{0pt}{0.25em}{.25em}
\setlength{\parindent}{0pt}

\definecolor{blueishgray}{HTML}{6c7f93}
\definecolor{darkgray}{HTML}{494c4e}
\definecolor{datecolor}{HTML}{999999}
\usepackage{tabularx}
\setlist{nolistsep}
\begin{document}
\color{darkgray}
\vspace*{-.25in}
\pagestyle{empty}

\noindent
\hspace*{-\dimexpr\oddsidemargin+1in\relax}%
\makebox[\paperwidth]{\color{blueishgray}\rule{\paperwidth}{20pt}}

% Header
\begin{center}
    {\huge \textbf{\textcolor{blueishgray}{Ian Hovde}}} \\
    \large \textcolor{blueishgray}{Software Engineer} \\
    \normalsize \textcolor{blueishgray}{ianhovde@gmail.com | Boston, MA | linkedin.com/in/ianhovde}
\end{center}

\noindent\rule{\linewidth}{.25pt}

% Summary
\section*{\textcolor{blueishgray}{Summary}}
Experienced software engineer with a proven track record in backend development, API design, and database management. 
Adept at leading complex migrations, optimizing systems for efficiency, and driving the adoption of modern development practices. 
Strong mentorship skills, fostering a collaborative and productive team atmosphere through clear communication and hands-on guidance. 
Passionate about delivering high-quality solutions that align with business objectives and exceed user expectations.

\section*{\textcolor{blueishgray}{Experience}}
\begin{tabularx}{\linewidth}{l|>{\raggedright\arraybackslash}X}
  \textbf{\textcolor{blueishgray}{SharpenCX}} & \textbf{\textcolor{blueishgray}{Software Engineer Team Lead}} \\ {\small \textcolor{datecolor}{06/2024-Present}} & 
  \begin{itemize}[leftmargin=*]
    \item Led the migration and upgrade of a multi-million dollar application stack with 70+ applications, transitioning from on-premises data centers to multiple AWS regions
    \item Utilized Docker, Bitbucket Pipelines, and AWS CDK to establish a PCI-compliant and fully redundant environment, ensuring scalability and reliability
    \item Managed a team of 5 engineers across 3 product stacks, facilitating standups, bi-weekly one-on-ones, and performance reviews to drive team alignment and individual growth.
    \item Reviewed and approved pull requests to ensure high code quality and compliance with security standards, safeguarding sensitive data including PCI and HIPAA information.
  \end{itemize} \\
  \textbf{\textcolor{blueishgray}{SharpenCX}} & \textbf{\textcolor{blueishgray}{Software Engineer ll}} \\ {\small \textcolor{datecolor}{10/2023-05/2024}} &
  \begin{itemize}[leftmargin=*]
    \item Implemented company-wide adoption of CI/CD pipelines using Bitbucket Pipelines. 
    \item Aided in backend development for a new customer facing product (ExpressJS, TypeScript), advancing it from Beta to GA.
    \item Managed and executed all legacy production releases, ensuring stability and adherence to test plans.
    \item Evaluated incoming Jira tickets to assess priority and provide time estimates for completion.
  \end{itemize} \\
  \textbf{\textcolor{blueishgray}{Plum Voice}} & \textbf{\textcolor{blueishgray}{Senior Software Engineer}} \\ {\small \textcolor{datecolor}{03/2023-09/2023}} &
  \begin{itemize}[leftmargin=*]
    \item Primary engineer on core web and voice processing application, utilized by the entire customer base, handling up to 10,000 concurrent connections during peak traffic (PHP/JS).
    \item Shipped 20+ releases on a weekly cadence, enhancing customers' web and voice experience with minimal service disruption.
    \item Contributed to AI product development on a modern stack (Python FastAPI).
    \item Coordinated and ran code review meeting among team members to ensure company and data security best practices were being met in a relaxed collaborative environment.
  \end{itemize} \\
  \textbf{\textcolor{blueishgray}{Plum Voice}} & \textbf{\textcolor{blueishgray}{Software Engineer}} \\ {\small \textcolor{datecolor}{09/2021-02/2023}} &
  \begin{itemize}[leftmargin=*]
    \item Engineered multiple features for core voice application, integrating live with AWS DynamoDB, AWS S3, AWS Polly, and Google Dialogflow (PHP).
    \item Redesigned and optimized logs database with PostgreSQL, enhancing capacity and query speed.
    \item Contributed to core application upgrade from PHP5.3 to PHP7.
    \item Supervised and mentored interns, assigning daily tasks, fostering problem-solving skills, conducting performance reviews, and providing ongoing support.
  \end{itemize} \\
  \textbf{\textcolor{blueishgray}{Plum Voice}} & \textbf{\textcolor{blueishgray}{Junior Software Engineer}} \\ {\small \textcolor{datecolor}{09/2020-08/2021}} &
  \begin{itemize}[leftmargin=*]
    \item Designed and coded RESTful API endpoints, enhancing customer control and accelerating information retrieval for applications.
    \item Architected and developed custom PHP voice applications per customer specifications.
    \item Provided Tier 3 support for main product stack, including on-call responsibilities.
  \end{itemize} \\
\end{tabularx}

\section*{\textcolor{blueishgray}{Skills}}
Languages: JavaScript (NodeJS, ExpressJS, Bun, VueJS), Python (FastAPI, Flask), PHP (Laravel, Koseven) \\
Databases: SQL (MySQL, Postgres), NoSQL (DynamoDB, MongoDB, CouchDB) \\
Tools: IaC (AWS CDK), CI/CD (CircleCI, Bitbucket Pipelines, Github Actions), RabbitMQ, Redis, Docker, Git

\section*{\textcolor{blueishgray}{Education}}
\begin{tabularx}{\linewidth}{l|>{\raggedright\arraybackslash}X}
    {\small \textcolor{datecolor}{09/2016-08/2020}} & \textbf{\textcolor{blueishgray}{Wentworth Institute of Technology} | BA: Computer Engineering} \\  & Magna Cum Laude
\end{tabularx}

\end{document}
